SFJ: An implementation of Semantic Featherweight Java

### 2020-02-19 conference/paper.tex
packages
running authors and title
restructuring the paper

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath}
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\title{SFJ: An implementation of Semantic Featherweight Java}
%\titlerunning{Abbreviated paper title}

\author{Artem Usov \and Ornela Dardha\orcidID{0000-0001-9927-7875}}

%\authorrunning{F. Author et al.}

@@

@@

\subsubsection{Sample Heading (Third Level)}
Only two levels of headings should be numbered. Lower level headings remain unnumbered; they are 
formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of headings. Table~\ref{tab1} gives a 
summary of all heading levels.

\begin{table}
    \caption{Table captions should be placed above the tables.}
    \label{tab1}
    \begin{tabular}{|l|l|l|}
        \hline
        Heading level     & Example                                          & Font size and style \\
        \hline
        Title (centered)  & {\Large\bfseries Lecture Notes}                  & 14 point, bold      \\
        1st-level heading & {\large\bfseries 1 Introduction}                 & 12 point, bold      \\
        2nd-level heading & {\bfseries 2.1 Printing Area}                    & 10 point, bold      \\
        3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold      \\
        4th-level heading & {\itshape Lowest Level Heading.} Text follows    & 10 point, italic    \\
        \hline
    \end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separateline.

\begin{equation}
    x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and schemas. Whenever possible, use 
vector graphics instead.

%\begin{figure}
%   \includegraphics[width=\textwidth]{fig1.eps}
%  \caption{A figure caption is always placed below the illustration.
%     Please note that short captions are centered, while long ones are
%     justified by the macro package automatically.} \label{fig1}
%\end{figure}

\begin{theorem}
    This is a sample theorem. The run-in heading is set in bold, while
    the following text appears in italics. Definitions, lemmas,
    propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
    Proofs, examples, and remarks have the initial word in italics,
    while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{Dardha2017}.

\bibliographystyle{splncs04}
\bibliography{paper}

>>>>

\documentclass[runningheads]{llncs}
%%%%%%%%%%%%%%%%%%%%%%%%
%PACKAGES
%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
%\usepackage{marvosym}
%\usepackage{txfonts}
%\usepackage{multicol}
\usepackage{proof-dashed}
\usepackage{graphicx}
\usepackage{listings}

% Non standard
\usepackage{varacca}
\input semmacros
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\title{SFJ: An implementation of Semantic Featherweight Java}
\titlerunning{SFJ}

\author{Artem Usov \and Ornela Dardha\orcidID{0000-0001-9927-7875}}
\authorrunning{A. Usov and O. Dardha}

@@

\section{Semantic Subtyping for Featherweight Java}

\section{SFJ: Design and Implementation}

@@

The following bibliography provides
a sample reference list with entries for journal
articles~\cite{Dardha2017}.

\section{Related Work and Conclusion}

%% References
\bibliographystyle{splncs04}
\bibliography{paper}
